---
output: github_document
---

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/septimanr)](https://cran.r-project.org/package=septimanr)
[![Travis-CI Build Status](https://travis-ci.org/ijlyttle/septimanr.svg?branch=master)](https://travis-ci.org/ijlyttle/septimanr)
appveyor.com/project/ijlyttle/septimanr)
[![Coverage Status](https://img.shields.io/codecov/c/github/ijlyttle/septimanr/master.svg)](https://codecov.io/github/ijlyttle/septimanr?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# septimanr

The goal of septimanr is to ...

## Installation

You can install septimanr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ijlyttle/septimanr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Code of Conduct 

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
